---
name: ""
surname: "Gabriel Mello Silva"
position: "Machine Learning Engineer"
address: "São Paulo, Brazil"
www: "gabriel-msilva.github.io"
email: "gabriel.zyx@gmail.com"
github: "gabriel-msilva"
linkedin: "gabriel-mello-silva"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "0a75ad"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(readr)
library(lubridate)
```

# About me

  * Experience in **building and deploying** Machine Learning models and data visualizations.
  * Passionate about **teaching** and highly value **efficient communication and organization** between teammates. 

# Experience

```{r experience}
experience <- read_csv("../data/experience.csv")
activities <- read_csv("../data/experience-activities.csv")
employers <- read_csv("../data/employers.csv")

format_ym <- function(.date) {
  if_else(
    is.na(.date), 
    "current",
    paste(year(.date), month(.date, label = TRUE))
  )
}

experience %>% 
  mutate(begin = lubridate::ym(begin), end = lubridate::ym(end)) %>% 
  left_join(activities, by = "job_id") %>% 
  left_join(employers, by = "employer_id") %>% 
  arrange(desc(begin)) %>% 
  detailed_entries(
    what = job_title,
    when = glue::glue("{format_ym(begin)} - {format_ym(end)}"),
    with = employer,
    where = glue::glue("{city}, {country}"),
    why = activities
  )
```

# Personal projects

```{r personal-projects}
projects <- tribble(
  ~ title, ~year, ~ description, ~url,
  "melloc", 2022, glue::glue("Personal blog about (Data) Science (website at \\url{gabriel-msilva.github.io/melloc})", .open = "<", .close = ">"), NA_character_,
  "fractal-sets", 2022, "Optimized functions to plot Mandelbrot and quadratic Julia sets", NA_character_,
  "covid-19", 2021, "Data analysis report of early COVID-19 data", NA_character_,
  "relevant-facts", 2020, "Data Science project about relevant facts for insider trading identification", NA_character_,
  "Where is the data scientist?", 2019, "Entry for \\textit{2018 Kaggle Machine Learning \\& Data Science Survey}",  "www.kaggle.com/code/gabrielmsilva/where-is-the-data-scientist"
) %>%
  mutate(url = if_else(is.na(url), glue::glue("github.com/gabriel-msilva/{title}"), url))

projects %>% 
  brief_entries(
    what = glue::glue("\\textbf{<title>}: <description> \\newline \\url{<url>}", .open = "<", .close = ">"), 
    when = year, 
    .protect = FALSE
  )
```

# Education

```{r education}
education <- read_csv("../data/education.csv")
institutions <- read_csv("../data/education-institutions.csv")

write_abbreviation <- function(.abbrv) {
  if_else(
    !is.na(.abbrv),
    glue::glue("({.abbrv})"),
    ""
  )
}

education %>% 
  left_join(institutions, by = "institution_id") %>% 
  detailed_entries(
    what = glue::glue("{degree} in {area}"),
    when = glue::glue("{begin} - {end}"),
    with = glue::glue("{name} {write_abbreviation(abbreviation)}"),
    where = glue::glue("{city}, {country}")
  )
```

# Courses

```{r courses}
courses <- read_csv("../data/courses.csv") %>% 
  mutate(end = lubridate::ym(end))

courses %>% 
  arrange(desc(end)) %>% 
  detailed_entries(
    what = course_name,
    when = glue::glue("{format_ym(end)}"),
    with = institution
  )
```

# Skills

```{r skills}
tribble(
  ~ skill, ~ contents,
  "Programming languages", "Python, R, C#, SQL, Spark, Bash",
  "Software development", "source control (Git), CI/CD (GitHub Actions, GoCD, Jenkins), unit tests, Python packaging (PIP/Conda), documentation websites",
  "Cloud computing", "AWS, Docker, Kubernetes",
  "Communication", "presentations, data visualization, data analysis reports, dashboard design"
) %>% 
  detailed_entries(what = contents, with = skill)
```

# Languages

```{r languages}
tribble(
  ~ language, ~ level,
  "Portuguese \\hspace{12 mm}  English \\hspace{13 mm}Spanish", 
  "Native \\hspace{23 mm} Fluent \\hspace{15.5 mm} Advanced",
) %>% 
  detailed_entries(what = level, with = language, .protect = FALSE)
```

# Publications

Publications available for download at [www.researchgate.net/profile/Gabriel-Mello-Silva](www.researchgate.net/profile/Gabriel-Mello-Silva).

```{r publications}
bibliography_entries("congress.bib") %>%
  arrange(desc(author$family), issued)
```

